---
title: "Homework #3"
author: "Alan Jones"
date: "February 15, 2017"
output:
  word_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```
```{r}
White_wines<-read.csv("White_wines.csv")
```

```{r}
summary(White_wines)
```

```{r}
#examine each variable in a univariate graph
variable.names(White_wines)
hist(White_wines$chlorides)
hist(White_wines$fixed.acidity)
hist(White_wines$volatile.acidity)
hist(White_wines$citric.acid)
hist(White_wines$residual.sugar)
hist(White_wines$free.sulfur.dioxide)
hist(White_wines$total.sulfur.dioxide)
hist(White_wines$density)
hist(White_wines$pH)
hist(White_wines$sulphates)
hist(White_wines$alcohol)
hist(White_wines$quality)
```

```{r}
#To get multivariate graphs
library(car)
scatterplotMatrix(~fixed.acidity + volatile.acidity + citric.acid, data=White_wines)
scatterplotMatrix(~residual.sugar + chlorides + free.sulfur.dioxide + total.sulfur.dioxide, data=White_wines)
scatterplotMatrix(~density + pH + sulphates + alcohol, data=White_wines)
```

```{r}
#To examine regression
RegModel.1 <- 
  lm(quality~alcohol+chlorides+citric.acid+density+fixed.acidity+free.sulfur.dioxide+pH+residual.sugar+sulphates+total.sulfur.dioxide+volatile.acidity,
   data=White_wines)
summary(RegModel.1)
```
```{r}
#To further examine regression
RegModel.1 <- 
  lm(quality~alcohol+density+fixed.acidity+free.sulfur.dioxide+pH+residual.sugar+sulphates+volatile.acidity,
   data=White_wines)
summary(RegModel.1)
```

A regression approach can be used because the order of preferences is preserved. The matrix is used for classification analysis. The results indicate that an increase in alcohol leads to higher quality scores of wine. Sulphates are an important factor in quality as well. White wine is also positively marked by higher citric acid and residual sugar levels. A decrease in quality is seen with higher volatile acidity scores. White wine quality scores are, therefore, most impacted by sulphates, citric acid, residual sugar levels, and alcohol being higher. 